Making use of spatially biased variables in ecosystem condition accounting – a GIS based workflow

### 2024-06-06 manuscript/Appendix B - source code.qmd
rename appendices

| id  | Variable code         | Variable name                                    | Measurement unit                                                                         | Description                                                                                                                                                       | Reference                                |
|------------|------------|------------|------------|--------------|------------|
| 1   | 7FA                   | Prevalence of alien species                      | Unit-less, ordinal, non-linear scale from 1 (no alien species) to 7 (only alien species) | The fraction of the species composition made up from alien species                                                                                                | @runehalvorsen2019                       |
| 2   | 7SE                   | Human caused abrasion or abrasion-caused erosion | Unit-less, ordinal, non-linear scale from 1 to 4.                                        | Measures the frequency of imagined 4 m^2^ quadrats laid over the area that has some sign of abrasion                                                              | @runehalvorsen2019                       |
| 3   | PRSL                  | *as above*                                       | Unit-less, ordinal, non-linear scale from 0 to 7.                                        | Same as 7SE, but recorded at a higher resolution                                                                                                                  | @norwegian_environmental_agency_protocol |
| 4   | 7TK                   | Tracks from large vehicles                       | Unit-less, ordinal, non-linear scale from 1 to 4.                                        | Measures the frequency of imagined 100 m^2^ quadrats laid over the area that has some signs of vehicle tracks                                                     | @runehalvorsen2019                       |
| 5   | PRTK                  | *as above*                                       | Unit-less, ordinal, non-linear scale from 0 to 7.                                        | Same as 7TK, but recorded at a higher resolution                                                                                                                  | @norwegian_environmental_agency_protocol |
| 6   | 7GR-GI                | Trenching intensity                              | Unit-less, ordinal scale from 1 to 5                                                     | Describes the effect that drainage ditches is estimate to have on the species composition and environmental variables ones the system reached its new equilibrium | @norwegian_environmental_agency_protocol |
| 7   | Infra-structure Index | Infrastructure Index                             | Unit-less linear scale from 0 to 13.2                                                    | Unit-less index ranging from from 0 to 13.2                                                                                                                       | @erikstad_index_2023                     |
| 8   | HIA                   | Homogeneous Impact Area                          | Ordinal, non-linear scale from 1 to 4                                                    | A categorical representation of the infrastructure index                                                                                                          | this paper                               |

@@

This manuscript is written in Quarto, and the source file (Appendix B) also contains code for all the analyses underlying this study, including data exploration and cleaning.
For a rendered version of the source file, with all code and calculation visible, see Appendix C. The source files and the data are also located on GitHub (https://github.com/anders-kolstad/HIAs) and will be archived on Zenodo with a stable doi at time of submission.
The exception is the large nature type survey data, which was downloaded locally, but which is freely available (see @norwegian_environmental_agency_naturtyper_2024).

>>>>

| id  | Variable code         | Variable name                                    | Measurement unit                                                                         | Description                                                                                                                                                       | Reference                                |
|------------|------------|------------|------------|------------|------------|
| 1   | 7FA                   | Prevalence of alien species                      | Unit-less, ordinal, non-linear scale from 1 (no alien species) to 7 (only alien species) | The fraction of the species composition made up from alien species                                                                                                | @runehalvorsen2019                       |
| 2   | 7SE                   | Human caused abrasion or abrasion-caused erosion | Unit-less, ordinal, non-linear scale from 1 to 4.                                        | Measures the frequency of imagined 4 m^2^ quadrats laid over the area that has some sign of abrasion                                                              | @runehalvorsen2019                       |
| 3   | PRSL                  | *as above*                                       | Unit-less, ordinal, non-linear scale from 0 to 7.                                        | Same as 7SE, but recorded at a higher resolution                                                                                                                  | @norwegian_environmental_agency_protocol |
| 4   | 7TK                   | Tracks from large vehicles                       | Unit-less, ordinal, non-linear scale from 1 to 4.                                        | Measures the frequency of imagined 100 m^2^ quadrats laid over the area that has some signs of vehicle tracks                                                     | @runehalvorsen2019                       |
| 5   | PRTK                  | *as above*                                       | Unit-less, ordinal, non-linear scale from 0 to 7.                                        | Same as 7TK, but recorded at a higher resolution                                                                                                                  | @norwegian_environmental_agency_protocol |
| 6   | 7GR-GI                | Trenching intensity                              | Unit-less, ordinal scale from 1 to 5                                                     | Describes the effect that drainage ditches is estimate to have on the species composition and environmental variables ones the system reached its new equilibrium | @norwegian_environmental_agency_protocol |
| 7   | Infra-structure Index | Infrastructure Index                             | Unit-less linear scale from 0 to 13.2                                                    | Unit-less index ranging from from 0 to 13.2                                                                                                                       | @erikstad_index_2023                     |
| 8   | HIA                   | Homogeneous Impact Area                          | Ordinal, non-linear scale from 1 to 4                                                    | A categorical representation of the infrastructure index                                                                                                          | this paper                               |

@@

This manuscript is written in Quarto, and the source file (Appendix B) also contains code for all the analyses underlying this study, including data exploration and cleaning.
For a rendered version of the source file, with all code and calculation visible, see Appendix C. The source files and the data are also located on GitHub (https://github.com/anders-kolstad/HIAs) with an archived stable version on Zenodo (doi:10.5281/zenodo.11504703).
The exception is the large nature type survey data, which was downloaded locally, but which is freely available (see @norwegian_environmental_agency_naturtyper_2024).
